The Chemistry Development Kit (CDK) \cdkversion{}: atom typing, depiction, molecular formulas, and substructure searching

### 2017-04-23 article.tex

@@

\subsection*{Table ? - Summary of systematic benchmark comparing v1.4.19 to \cdkversion{}.}\label{tab:benchmark}
  The total elapsed real time was measured with the GNU time utility. The 
  throughput is reported in molecules per minute (k=thousand, m=million) as a 
  relatable metric.
  This throughput was calculated by taking the total elapsed
  time and dividing it by the number of molecule in the dataset (42704 for 
  ChEBI 149, and 1678393 for ChEMBL 22.1). Nine records skipped for SMILES input for
  \cdkversion{} is because the parser now validates on read and both ChEBI/
  ChEMBL contain invalid SMILES (9 each, they are different records). The SDfile skips
  were molecules in ChEBI with query bonds. The ChEBI SMILES input contains 
  2107 blank (but valid) inputs, this accounts for the majority skipped 
  in v1.4.19. Additional skipped records were due to failures somewhere else,
  ChEBI contains some exotic molecules causing a few skipped records where
  ChEMBL has none.

@@

\multirow{4}{*}{rings-mark} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 22.91s & 106.3K & 9 & 1.03s & 2.4M & 22.24\\

@@

\multirow{4}{*}{rings-sssr} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 27.4s & 88.9K & 9 & 1.48s & 1.6M & 18.51\\

@@

\multirow{4}{*}{rings-all} & \multirow{2}{*}{ChEBI 149} & smi & 2126 & 45.28s & 53.8K & 26 & 1.27s & 1.9M & 35.65\\

@@

\multirow{4}{*}{convert-ofmtsmi} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 35.63s & 68.4K & 16 & 1.37s & 1.8M & 26.01\\

@@

\multirow{4}{*}{convert-ofmtsdf} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 32.42s & 75.1K & 9 & 10.33s & 235.8K & 3.14\\

@@

\multirow{4}{*}{convert--gen2d-ofmtsdf} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 24m28.02s & 1.7K & 9 & 35.7s & 68.2K & 41.12\\

@@

\multirow{4}{*}{fpgen-type=path} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 1m14.5s & 32.7K & 26 & 8.22s & 296.3K & 9.06\\

@@

\multirow{4}{*}{fpgen-type=maccs} & \multirow{2}{*}{ChEBI 149} & smi & 2150 & 1h37m35s & 416 & 9 & 19.8s & 123K & 295.71\\

@@

\multirow{4}{*}{fpgen-type=circ} & \multirow{2}{*}{ChEBI 149} & smi & 0 & NA & - & 9 & 4.47s & 544.9K & 0\\

@@

\begin{tabular}{lllrclrcll}
Benchmark  & \multicolumn{2}{c}{Data Set} & \multicolumn{3}{c}{CDK 1.4.19} & \multicolumn{3}{c}{CDK \cdkversion{}} & Improvement \\
           &          &              & Skip & Time & Per Min & Skip  & Time  & Per Min \\
\hline
\multirow{4}{*}{countheavy}  & \multirow{2}{*}{ChEBI 149}  & smi & 0 & 0s & - & 0 & 0s & - & \\
 &  & sdf & 0 & 0s & - & 0 & 0s & - & \\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 0 & 0s & - & 0 & 0s & - & \\
 &  & sdf & 0 & 0s & - & 0 & 0s & - & \\
\hline
\multirow{4}{*}{rings-mark}  & \multirow{2}{*}{ChEBI 149}  & smi & 0 & 0.4s & 6.1M & 0 & 0.06s & 40.6M & 6.7\\
 &  & sdf & 0 & 1.5s & 1.7M & 0 & 0.18s & 14.2M & 8.3\\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 0 & 6.48s & 15.5M & 0 & 5.81s & 17.3M & 1.1\\
 &  & sdf & 0 & 54.72s & 1.8M & 0 & 7.72s & 13M & 7.1\\
\hline
\multirow{4}{*}{rings-sssr}  & \multirow{2}{*}{ChEBI 149}  & smi & 0 & 4.89s & 498.1K & 0 & 0.51s & 4.8M & 9.6\\
 &  & sdf & 0 & 4.63s & 553.4K & 0 & 0.33s & 7.8M & 14\\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 0 & 3m25.32s & 490.5K & 0 & 15.9s & 6.3M & 12.9\\
 &  & sdf & 0 & 3m52.29s & 433.5K & 0 & 16.93s & 5.9M & 13.7\\
\hline
\multirow{4}{*}{rings-all}  & \multirow{2}{*}{ChEBI 149}  & smi & 14 & 22.77s & 107K & 17 & 0.3s & 8.1M & 75.9\\
 &  & sdf & 16 & 29.35s & 87.3K & 15 & 0.38s & 6.7M & 77.2\\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 88 & 4m0.9s & 418K & 0 & 14.31s & 7M & 16.8\\
 &  & sdf & 90 & 4m48.35s & 349.2K & 0 & 11.76s & 8.6M & 24.5\\
\hline
\multirow{4}{*}{cansmi}  & \multirow{2}{*}{ChEBI 149}  & smi & 0 & 14.07s & 173.1K & 0 & 0.86s & 2.8M & 16.4\\
 &  & sdf & 35 & 13.94s & 183.8K & 1 & 1.02s & 2.5M & 13.7\\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 14 & 5m54.56s & 284K & 0 & 30.24s & 3.3M & 11.7\\
 &  & sdf & 0 & 5m42.53s & 294K & 0 & 37.63s & 2.7M & 9.1\\
\hline
\multirow{4}{*}{convert-ofmtsmi}  & \multirow{2}{*}{ChEBI 149}  & smi & 0 & 13.12s & 185.7K & 7 & 0.4s & 6.1M & 32.8\\
 &  & sdf & 35 & 13.7s & 187K & 4 & 0.46s & 5.6M & 29.8\\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 14 & 5m46.72s & 290.4K & 25 & 16.48s & 6.1M & 21\\
 &  & sdf & 0 & 5m42.09s & 294.4K & 4 & 20.12s & 5M & 17\\
\hline
\multirow{4}{*}{convert-ofmtsdf}  & \multirow{2}{*}{ChEBI 149}  & smi & 0 & 9.91s & 245.8K & 0 & 9.36s & 260.2K & 1.1\\
 &  & sdf & 13 & 9.79s & 261.7K & 4 & 10.74s & 238.6K & 0.9\\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 0 & 5m46.52s & 290.6K & 0 & 5m18.49s & 316.2K & 1.1\\
 &  & sdf & 1 & 5m34.04s & 301.5K & 0 & 5m43.69s & 293K & 1\\
\hline
\multirow{4}{*}{convert--gen2d-ofmtsdf}  & \multirow{2}{*}{ChEBI 149}  & smi & 0 & 24m5.51s & 1.7K & 0 & 34.73s & 70.1K & 41.6\\
 &  & sdf & 13 & 35m4.82s & 1.2K & 4 & 38.33s & 66.8K & 54.9\\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 0 & 3h18m28s & 8.5K & 0 & 17m50.42s & 94.1K & 11.1\\
 &  & sdf & 1 & 5h55m13s & 4.7K & 0 & 18m46.89s & 89.4K & 18.9\\
\hline
\multirow{4}{*}{fpgen-type=path}  & \multirow{2}{*}{ChEBI 149}  & smi & 0 & 51.99s & 46.9K & 17 & 7.25s & 336K & 7.2\\
 &  & sdf & 0 & 1m44.96s & 24.4K & 15 & 7.92s & 323.5K & 13.3\\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 0 & 26m23.5s & 63.6K & 0 & 5m23.08s & 311.7K & 4.9\\
 &  & sdf & 0 & 35m34.44s & 47.2K & 0 & 4m59.81s & 335.9K & 7.1\\
\hline
\multirow{4}{*}{fpgen-type=maccs}  & \multirow{2}{*}{ChEBI 149}  & smi & 38 & 1h37m12s & 418 & 0 & 18.83s & 129.4K & 309.7\\
 &  & sdf & 48 & 1h44m10s & 410 & 0 & 18.58s & 137.9K & 336.4\\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 214 & 20h16m18s & 1.4K & 0 & 13m14.94s & 126.7K & 91.8\\
 &  & sdf & 225 & 24h38m29s & 1.1K & 0 & 12m34.6s & 133.5K & 117.6\\
\hline
\multirow{4}{*}{fpgen-type=circ}  & \multirow{2}{*}{ChEBI 149}  & smi & -2112 &  & - & 0 & 3.5s & 695.9K & \\
 &  & sdf & 0 &  & - & 0 & 3.29s & 778.8K & \\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 0 &  & - & 0 & 2m33.51s & 656K & \\
 &  & sdf & 0 &  & - & 0 & 2m52s & 585.5K & \\
\hline
\end{tabular}

>>>>

\subsection*{Systematic Benchmark}

A systematic benchmark was performed to evaluate and quantify 
performance improvements from v1.4.19 to \cdkversion{}. The benchmark is 
divided into several cheminformatics tasks for common use cases. Each task 
was evaluated on input from ChEBI 149 \cite{ChEBI13} and ChEMBL 22.1 
\cite{ChEMBL14} as both SMILES and SDF.

The benchmark was run on Java SE 8, Cent OS 7, Intel Core i7-4790 CPU @ 
3.60GHz with 16 GB of RAM. The code to run the benchmark is available in 
the supplementary material allowing numbers to be recorded on the
reader's system.

The results of benchmark are summarised in Table 6 and 7. The total elapsed
times are reported in Table 6, Table 7 subtracts the first tasks results 
(Count Heavy Atoms) to provide a comparable measure without the overhead of
input read time. The throughput as molecules per minute is reported but is less
accurate for v. fast running tasks.

\subsubsection*{Count Heavy Atoms}

This task highlights improvements in raw read performance. Each record is read
in to a resident memory connection table and the number of heavy (non-hydrogen)
atoms counted by iterating over the atoms sequentially.

The improvement on this task is most noticeable for SMILES input, previously
it would take more than 8 minutes to read ChEMBL 22.1 but this is reduced
to only 12 seconds. On top of this improvement SMILES input is now validated 
and assigned a Kekul$\mathrm{\acute{e}}$ structure. This identifies 9 invalid
entries in ChEBI and another 9 in ChEMBL. Most of these rejected SMILES
are due to the wrong encoding of Cis/Trans double bond stereochemistry at ring 
closures. The ChEBI 149 SMILES input has 2107 empty records that v1.4.19 skip,
\cdkversion{} simply reads these as empty molecules. Input from SDF also 
improved from $\sim$3 minutes to $\sim$1 minute for ChEMBL. The SDF input in
\cdkversion{} now includes perception of stereochemistry and reading CTfile 
Sgroups. There are 9 entries from ChEBI's SDF that are rejected because they 
contain CTfile query features (e.g. any bond order).

\subsubsection*{Rings}

Ring perception is a fundamental step in many other algorithms. 
The rings task is divided as three subtasks: mark, sssr, and all.

\textbf{-mark}, The first subtask measures the performance in marking 
ring membership and reporting the number of ring bonds in each record.
This requires a linear algorithm based on a depth first search. 
The original code used a weighted spanning tree to compute the membership in 
linearithmic time. The run times are similar for these datasets (Table
7), larger differences are seen for more complex cage molecules such fullerenes
\cite{May2014}.

\textbf{-sssr}, The second subtask computes the Smallest Set of Smallest Rings 
(SSSR) and reports the size of the SSSR (circuit rank) for each record. Although 
circuit rank can be computed more efficiently 
with a linear traversal (counting DFS back-edges) or with Euler's 
polyhedron formula we are testing the time to enumerate the SSSR set. In general
SSSR is considered unfavourable due to the 
non-uniqueness of the set and need for Gaussian matrix elimination (cubic 
runtime). With some bookkeeping the time spent in the matrix elimination has been
reduced~\cite{May2014}. For ChEMBL we see the time to generate the SSSR is now
$\sim$16 seconds when it previously took around $\sim$3.5 minutes (Table 7).

\textbf{-all}, The third subtask counts the number of all rings up to or equal
to size 12. This includes rings that encompass other smaller rings, for 
example, 1H-indole has rings of size 5, 6, and 9. In general this problem is 
exponential and so an adjustable threshold or timeout is used to avoid problematic 
molecules. CDK v1.4.19 used a timeout based threshold (default 5 seconds) 
whilst \cdkversion{} uses a 
counter based on properties of algorithm~\cite{May2014}. In \cdkversion{} there
were 15/17\footnote{2 records from SDF use query bond features and are skipped
when read} records skipped from ChEBI that have complex cage-like ring systems 
(e.g. CHEBI:33611), no records in ChEMBL reached the threshold. By comparison in
v1.4.19 there were 14/16 records skipped from ChEBI and 88/90 in ChEMBL due to
reaching the time out. The number fluctuates here as a timeout based threshold 
depends on external factors such as CPU load.

The speed-up in \cdkversion{} is slightly better than the SSSR task. ChEMBL 
previously spent 4-5 minutes and now takes only $\sim$14 seconds (Table 7).
In \cdkversion{} finding all rings ($\leq$ 12 bonds) runs faster than the 
non-unique SSSR computation.

\subsection*{Canonical SMILES}

This task measures the generation of a Unique SMILES string. These can be
used to compare dataset intersection and exact lookup. From SMILES input
\cdkversion{} the total elapsed time is $\sim$20 times faster for both ChEBI
and ChEMBL. For ChEMBL it now takes just under 43 seconds to read, reorder, 
and write the SMILES compared to more than 14 minutes previously.

\subsection*{Convert}

This tasks tests the non-canonical conversion between SDF and SMILES input.

\textbf{-ofmt smi}: SMILES is a very compact means of storing connection tables, v1.4.19 could 
only write canonical SMILES, \cdkversion{} allows different SMILES flavours 
to be generated including a non-canonical variant. This task outputs
CXSMILES that includes additional fields such as repeat groups (used by some 
ChEBI entries). As
expected the v1.4.19 execution time is the same as for the Canonical SMILES 
task but \cdkversion{} can generate the non-canonical SMILES faster taking less
than 30 seconds for ChEMBL.

Assigning double-bond configurations in SMILES is 
non-trivial and \cdkversion{} has some safety checks, since the SMILES output is 
Keklu$\mathrm{\acute{e}}$ but input was aromatic, when the bond orders are 
assigned an extra double-bond may be accidental encoded in the SMILES output, 
this is sometimes acceptable but will currently report an error. A few errors (4
in ChEBI, 3 in ChEMBl) occur from Sgroup processing that have now been addressed.

\textbf{-ofmt sdf}: For writing SDF output there is minimal improvement from v1.14.19, when 
discounting improvements in read performance the SDF generation for ChEBI 
actually runs slightly slower than v1.4.19 (Table 7). This can be partially 
explained by the more comprehensive SDF generation that now writes Sgroups 
as well as computing values for atom parity and valence columns.

\textbf{-gen2d -ofmt sdf}: When writing SDF the only portable way to store stereochemistry is with the 
inclusion of coordinates, this is specified with the \texttt{-gen2d} option. 
The overhaul in layout generation discussed early provides better layouts but 
also included performance tweaks, in CDK v1.4.19 generating coordinates and 
writing an SDF for ChEMBL took almost 3.5 hours but now only takes just over
18 minutes.

\subsection*{Fingerprint Generation}

This task tests the generation of fingerprints for similarity and substructure
screening. Three different types of fingerprints were tested, a Daylight-like 
Hashed Path Fingerprint, MACCS-like 166 Keys, and Pipeline Pilot-like Hashed 
Circular Fingerprint (ECFP4). The task generates a hexadecimal FPS file that
can be used with chemfp~\cite{Dalke2013}.

\textbf{-type path}: Path based fingerprints encode paths of length 1...n. n was
choose to be 6 for this benchmark. Path based fingerprints can be used for both
substructure and similarity screening. The algorithm was
tweaked for \cdkversion{} to hash the paths without pre-computing all paths
upfront and without needing to generate character strings before hashing. An
abort threshold was also placed to catch pathological molecules (shown as 
skipped in ChEBI) that previously took a long time - this will be optimized and 
removed in future. The time to encode ChEMBL previously took 26-35 minutes now 
only takes $\sim$5 minutes.

\textbf{-type maccs}: The CDK MACCS fingerprint uses 166 keys to encode
features of a structure and can be used for similarity searching. This encoding
uses different aspects of the library including ring perception and the new
aromaticity perception but the speed is primarily dependant on SMARTS matching 
performance. Generating the fingerprint previously took almost 1 day for ChEMBL 
and 2 hours for ChEBI. This has been reduced to less than 
15 minutes for ChEMBL and less than 30 seconds for ChEBI.

\textbf{-type circ}: Circular fingerprints can only be used for similarity and
could not be generated in v1.4.19. However, the fingerprints are known to perform
well for retrieval performance~\cite{OBoyle2016}. The times are included here 
to show they are faster to calculate than path or MACCS-like keys and therefore
recommended. CDK includes two implementations based on signatures or extended 
connectivity~\cite{Clark2014}.

\subsubsection*{Benchmark Summary}

In all tasks, the total elapsed time is better in \cdkversion{} compared to 
v1.4.19. On many tasks the improvement is more than ten times faster.
Not only is the execution time improved but improvements in robustness and 
correctness means \cdkversion{} is often doing much more work than the 
equivalent procedures in v1.4.19.

@@

\subsection*{Table 6 - Summary of systematic benchmark comparing v1.4.19 to \cdkversion{}.}\label{tab:benchmark}
  The total elapsed \textit{real} time was measured with the unix time utility. The 
  throughput is reported in molecules per minute (K=thousand, M=million) as a 
  relatable metric.
  This throughput was calculated by taking the total elapsed
  time and dividing it by the number of molecule in the dataset (42704 for 
  ChEBI 149, and 1678393 for ChEMBL 22.1). The ChEBI SMILES input contains 
  2107 blank (but valid) inputs, this accounts for the majority skipped 
  in v1.4.19. The throughput calculation was adjust to account for this.

@@

\multirow{4}{*}{\shortstack[l]{rings \\ -mark}} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 22.91s & 106.3K & 9 & 1.03s & 2.4M & 22.24\\

@@

\multirow{4}{*}{\shortstack[l]{rings \\ -sssr}} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 27.4s & 88.9K & 9 & 1.48s & 1.6M & 18.51\\

@@

\multirow{4}{*}{\shortstack[l]{rings \\ -all}} & \multirow{2}{*}{ChEBI 149} & smi & 2126 & 45.28s & 53.8K & 26 & 1.27s & 1.9M & 35.65\\

@@

\multirow{4}{*}{\shortstack[l]{convert \\ -ofmt smi}} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 35.63s & 68.4K & 16 & 1.37s & 1.8M & 26.01\\

@@

\multirow{4}{*}{\shortstack[l]{convert \\ -ofmt sdf}} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 32.42s & 75.1K & 9 & 10.33s & 235.8K & 3.14\\

@@

\multirow{4}{*}{\shortstack[l]{convert \\ -gen2d \\ -ofmt smi}} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 24m28.02s & 1.7K & 9 & 35.7s & 68.2K & 41.12\\

@@

\multirow{4}{*}{\shortstack[l]{fpgen \\ -type path}} & \multirow{2}{*}{ChEBI 149} & smi & 2112 & 1m14.5s & 32.7K & 26 & 8.22s & 296.3K & 9.06\\

@@

\multirow{4}{*}{\shortstack[l]{fpgen \\ -type maccs}} & \multirow{2}{*}{ChEBI 149} & smi & 2150 & 1h37m35s & 416 & 9 & 19.8s & 123K & 295.71\\

@@

\multirow{4}{*}{\shortstack[l]{fpgen \\ -type circ}} & \multirow{2}{*}{ChEBI 149} & smi & 0 & NA & - & 9 & 4.47s & 544.9K & 0\\

@@

\subsection*{Table 7 - Summary of systematic benchmark comparing v1.4.19 to \cdkversion{} without read times.}
\label{tab:benchmark-delta}
The number of records skipped and time to run the countheavy benchmark has been subtracted from Table 6. The remaining results provides a relative comparison without accounting for the overhead of reading the input.

\begin{tabular}{lllrclrcll}
\multirow{4}{*}{countheavy}  & \multirow{2}{*}{ChEBI 149}  & smi & 0 & 0s & - & 0 & 0s & - & \\
 &  & sdf & 0 & 0s & - & 0 & 0s & - & \\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 0 & 0s & - & 0 & 0s & - & \\
 &  & sdf & 0 & 0s & - & 0 & 0s & - & \\
\multirow{4}{*}{\shortstack[l]{rings \\ -mark}}  & \multirow{2}{*}{ChEBI 149}  & smi & 0 & 0.4s & 6.1M & 0 & 0.06s & 40.6M & 6.7\\
 &  & sdf & 0 & 1.5s & 1.7M & 0 & 0.18s & 14.2M & 8.3\\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 0 & 6.48s & 15.5M & 0 & 5.81s & 17.3M & 1.1\\
 &  & sdf & 0 & 54.72s & 1.8M & 0 & 7.72s & 13M & 7.1\\
\multirow{4}{*}{\shortstack[l]{rings \\ -sssr}}  & \multirow{2}{*}{ChEBI 149}  & smi & 0 & 4.89s & 498.1K & 0 & 0.51s & 4.8M & 9.6\\
 &  & sdf & 0 & 4.63s & 553.4K & 0 & 0.33s & 7.8M & 14\\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 0 & 3m25.32s & 490.5K & 0 & 15.9s & 6.3M & 12.9\\
 &  & sdf & 0 & 3m52.29s & 433.5K & 0 & 16.93s & 5.9M & 13.7\\
\multirow{4}{*}{\shortstack[l]{rings \\ -all}}  & \multirow{2}{*}{ChEBI 149}  & smi & 14 & 22.77s & 107K & 17 & 0.3s & 8.1M & 75.9\\
 &  & sdf & 16 & 29.35s & 87.3K & 15 & 0.38s & 6.7M & 77.2\\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 88 & 4m0.9s & 418K & 0 & 14.31s & 7M & 16.8\\
 &  & sdf & 90 & 4m48.35s & 349.2K & 0 & 11.76s & 8.6M & 24.5\\
\multirow{4}{*}{cansmi}  & \multirow{2}{*}{ChEBI 149}  & smi & 0 & 14.07s & 173.1K & 0 & 0.86s & 2.8M & 16.4\\
 &  & sdf & 35 & 13.94s & 183.8K & 1 & 1.02s & 2.5M & 13.7\\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 14 & 5m54.56s & 284K & 0 & 30.24s & 3.3M & 11.7\\
 &  & sdf & 0 & 5m42.53s & 294K & 0 & 37.63s & 2.7M & 9.1\\
\multirow{4}{*}{\shortstack[l]{convert \\ -ofmt smi}}  & \multirow{2}{*}{ChEBI 149}  & smi & 0 & 13.12s & 185.7K & 7 & 0.4s & 6.1M & 32.8\\
 &  & sdf & 35 & 13.7s & 187K & 4 & 0.46s & 5.6M & 29.8\\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 14 & 5m46.72s & 290.4K & 25 & 16.48s & 6.1M & 21\\
 &  & sdf & 0 & 5m42.09s & 294.4K & 4 & 20.12s & 5M & 17\\
\multirow{4}{*}{\shortstack[l]{convert \\ -ofmt sdf}}  & \multirow{2}{*}{ChEBI 149}  & smi & 0 & 9.91s & 245.8K & 0 & 9.36s & 260.2K & 1.1\\
 &  & sdf & 13 & 9.79s & 261.7K & 4 & 10.74s & 238.6K & 0.9\\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 0 & 5m46.52s & 290.6K & 0 & 5m18.49s & 316.2K & 1.1\\
 &  & sdf & 1 & 5m34.04s & 301.5K & 0 & 5m43.69s & 293K & 1\\
\multirow{4}{*}{\shortstack[l]{convert \\ -gen2d \\ -ofmt smi}}  & \multirow{2}{*}{ChEBI 149}  & smi & 0 & 24m5.51s & 1.7K & 0 & 34.73s & 70.1K & 41.6\\
 &  & sdf & 13 & 35m4.82s & 1.2K & 4 & 38.33s & 66.8K & 54.9\\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 0 & 3h18m28s & 8.5K & 0 & 17m50.42s & 94.1K & 11.1\\
 &  & sdf & 1 & 5h55m13s & 4.7K & 0 & 18m46.89s & 89.4K & 18.9\\
\multirow{4}{*}{\shortstack[l]{fpgen \\ -type path}}  & \multirow{2}{*}{ChEBI 149}  & smi & 0 & 51.99s & 46.9K & 17 & 7.25s & 336K & 7.2\\
 &  & sdf & 0 & 1m44.96s & 24.4K & 15 & 7.92s & 323.5K & 13.3\\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 0 & 26m23.5s & 63.6K & 0 & 5m23.08s & 311.7K & 4.9\\
 &  & sdf & 0 & 35m34.44s & 47.2K & 0 & 4m59.81s & 335.9K & 7.1\\
\multirow{4}{*}{\shortstack[l]{fpgen \\ -type maccs}}  & \multirow{2}{*}{ChEBI 149}  & smi & 38 & 1h37m12s & 418 & 0 & 18.83s & 129.4K & 309.7\\
 &  & sdf & 48 & 1h44m10s & 410 & 0 & 18.58s & 137.9K & 336.4\\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 214 & 20h16m18s & 1.4K & 0 & 13m14.94s & 126.7K & 91.8\\
 &  & sdf & 225 & 24h38m29s & 1.1K & 0 & 12m34.6s & 133.5K & 117.6\\
\multirow{4}{*}{\shortstack[l]{fpgen \\ -type circ}}  & \multirow{2}{*}{ChEBI 149}  & smi & 0 &  & - & 0 & 3.5s & 695.9K & \\
 &  & sdf & 0 &  & - & 0 & 3.29s & 778.8K & \\
 & \multirow{2}{*}{ChEMBL 22.1}  & smi & 0 &  & - & 0 & 2m33.51s & 656K & \\
 &  & sdf & 0 &  & - & 0 & 2m52s & 585.5K & \\
